Autonomous Aerial Exploration for Topological Mapping of Mars Environments

### 2018-06-11 Conference/SCITECH19/SCITECH19.tex
Fig. 5 split in 2 for each case

The simulation was run twice. Case 1 was as described in this paper. Case 2 was identical to Case 1, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} proved effective for level flight. The resulting occupancy grid maps and complete map entropy are shown in Figs. \ref{fig:mars3Dogm} and \ref{fig:mars3Dentropy}, respectively.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap1min.jpg}
        		\caption{Case 1: $1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap1min.jpg}
        		\caption{Case 2: $1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap2min.jpg}
        		\caption{Case 1: $2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap2min.jpg}
        		\caption{Case 2: $2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap5min.jpg}
        		\caption{Case 1: $5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap5min.jpg}
        		\caption{Case 2: $5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap10min.jpg}
        		\caption{Case 1: $10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap10min.jpg}
        		\caption{Case 2: $10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap15min.jpg}
        		\caption{Case 1: $15$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap20min.jpg}
        		\caption{Case 1: $20$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{The robot (red disk with arrow indicating laser direction) moves toward candidate poses (red arrows, more opaque for greater reward) while generating a 3D probabilistic occupancy grid map (cubes: greater opacity for greater occupancy probability) of the surface of Mars.}
\label{fig:mars3Dogm}
\end{figure}

@@

\todo{I wish we have a little more pages. Let's split Figure 5 into two, one for Case 1 and another for Case 2, where each case has more time instances. (Also, check the caption for (j)).
We can have another zoomed-in figure hat shows the aerial vehicle with the simulated measurements of the point clouds and the candidate poses more clearly}

>>>>

The simulation was run twice. Case 1 was as described in this paper. Case 2 was identical to Case 1, except the reduced map $ m_\text{reduced}$ is used when computing \refeqn{Iscan}. Case 2 is largely inspired by the promising results of~\cite{KauTakAiLee18}, where a projected map based on the same criteria as \refeqn{Proj3DMapComb} proved effective for level flight. The resulting occupancy grid maps for Case 1 and 2 are shown in Figs. \ref{fig:mars3DogmCase1} and \ref{fig:mars3DogmCase2}, respectively, and complete map entropy is illustrated in Fig. \ref{fig:mars3Dentropy}.

%\begin{figure}[!t]
%	\centering
%	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsFullMap1min.jpg}
%        		\caption{Case 1: $1$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap1min.jpg}
%        		\caption{Case 2: $1$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%	\centering
%	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsFullMap2min.jpg}
%        		\caption{Case 1: $2$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap2min.jpg}
%        		\caption{Case 2: $2$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%	\centering
%	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsFullMap5min.jpg}
%        		\caption{Case 1: $5$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap5min.jpg}
%        		\caption{Case 2: $5$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%	\centering
%	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsFullMap10min.jpg}
%        		\caption{Case 1: $10$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap10min.jpg}
%        		\caption{Case 2: $10$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%	\centering
%	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsFullMap15min.jpg}
%        		\caption{Case 1: $15$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[height=0.5\textwidth]{MarsFullMap20min.jpg}
%        		\caption{Case 1: $20$ min}
%		\vspace*{0.025\textwidth}
%    	\end{subfigure}
%\caption{The robot (red disk with arrow indicating laser direction) moves toward candidate poses (red arrows, more opaque for greater reward) while generating a 3D probabilistic occupancy grid map (cubes: greater opacity for greater occupancy probability) of the surface of Mars.}
%\label{fig:mars3Dogm}
%\end{figure}

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap1min.jpg}
        		\caption{$1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap2min.jpg}
        		\caption{$2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap3min.jpg}
        		\caption{$3$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap4min.jpg}
        		\caption{$4$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap5min.jpg}
        		\caption{$5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap10min.jpg}
        		\caption{$10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap15min.jpg}
        		\caption{$15$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsFullMap20min.jpg}
        		\caption{$20$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{In Case 1, the robot (red disk with arrow indicating laser direction) moves toward candidate poses (red arrows, more opaque for greater reward) based on expected entropy change of the 3D probabilistic occupancy grid map $m$ (cubes: greater opacity for greater occupancy probability) of the surface of Mars.}
\label{fig:mars3DogmCase1}
\end{figure}

\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap1min.jpg}
        		\caption{$1$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap2min.jpg}
        		\caption{$2$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap3min.jpg}
        		\caption{$3$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap4min.jpg}
        		\caption{$4$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
	\centering
	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap5min.jpg}
        		\caption{$5$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.49\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{MarsRdcdMap10min.jpg}
        		\caption{$10$ min}
		\vspace*{0.025\textwidth}
    	\end{subfigure}
\caption{In Case 2, the robot (red disk with arrow indicating laser direction) generates a 3D probabilistic occupancy grid map $m$ (cubes: greater opacity for greater occupancy probability), which is used to generate a reduced map $m_\text{reduced}$ based on \refeqn{Proj3DMapComb}. The robot moves toward candidate poses (red arrows, more opaque for greater reward) based on expected entropy change of $m_\text{reduced}$.}
\label{fig:mars3DogmCase2}
\end{figure}

@@

\todo{I wish we have a little more pages. We can have another zoomed-in figure hat shows the aerial vehicle with the simulated measurements of the point clouds and the candidate poses more clearly}
